---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GCSM

<!-- badges: start -->
[![R-CMD-check](https://github.com/liuyadong/GCSM/workflows/R-CMD-check/badge.svg)](https://github.com/liuyadong/GCSM/actions)
<!-- badges: end -->

The goal of GCSM is to implement the generic composite similarity measure (GCSM), described in "A generic composite measure of similarity between geospatial variables" by Liu et al. (2020) [doi:10.1016/j.ecoinf.2020.101169](https://doi.org/10.1016/j.ecoinf.2020.101169). This package also provides implements of SSIM and CMSC. Functions are given to compute composite similarity between vectors (e.g, `gcsm`), on spatial windows (e.g., `gcsm_sw`) or temporal windows (e.g., `gcsm_tw`). They are implemented in C++ with [RcppArmadillo](https://github.com/RcppCore/RcppArmadillo). OpenMP is used for parallel computing.

## Installation

You can install the package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("liuyadong/GCSM")
```
## Examples

Composite similarity between vectors:
```{r example}
library(GCSM)

x = runif(9)
gcsm(x, x)
cmsc(x, x)

# mean shift
gcsm(x, x - 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
cmsc(x, x - 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
gcsm(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
cmsc(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
## dissimilarity
y = 1 - x # y is the perfect antianalog of x
gcsm(y, x)
gcsm(y, x - 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
gcsm(y, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)

# random noise
noise = rnorm(9, mean = 0, sd = 0.1)
gcsm(x, x + noise, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
cmsc(x, x + noise, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
## dissimilariry
gcsm(y, x + noise, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
```

Composite similarity on spatial windows:
```{r}
x = matrix(runif(36), nrow = 6, ncol = 6)
gcsm_sw(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1, ksize = 3)
cmsc_sw(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1, ksize = 3)
ssim_sw(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1, ksize = 3)
```

Composite similarity on temporal windows:
```{r}
x = array(runif(81), dim = c(3, 3, 9))
gcsm_tw(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
cmsc_tw(x, x + 0.2, xmin = 0, xmax = 1, ymin = 0, ymax = 1)
```
